JMLR-14-133-4: Point-to-Point Reply

### 2015-01-05 pkg/partykit/inst/mloss/review4/p2p.tex
small improvements
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@674 255f4249-2263-4417-b1ea-8498779e27a7

The new \texttt{partykit::cforest} basically implements old functionality
using the new framework. The code-base is much denser now and the two
implementations were tested to return identical results (in situations where
is can be expected). It also allows a little more flexibility with respect
to probabilistic forecasts (via quantile regression forests) but is still
limited to trees with constant fits in the nodes. Therefore, the challenge
of adding flexible support for forests of model-based is still open and
definitively a research project in its own right because also the underlying
theory has to be developed.

Certainly, much more work can be done on general software for random forests
as well as improvements of the \texttt{cforest} function.  We intend to do
so in the future by tackling some of the open conceptual issues described in
our previous replies.  But, the current \texttt{partykit::cforest} function
clearly shows that also implementations of random forests will benefit from
the unified tree infrastructure established in the partykit package.

>>>>

The new \texttt{partykit::cforest} basically implements old functionality
using the new framework. The code base is much denser now and the two
implementations were tested to return identical results (in situations where
this can be expected). It also allows a little more flexibility with respect
to probabilistic forecasts (via quantile regression forests) but is still
limited to trees with constant fits in the nodes. Therefore, the challenge
of adding flexible support for forests of model-based trees is still open and
definitively a research project in its own right because also the underlying
theory has to be developed.

Certainly, much more work can be done on general software for random forests
as well as improvements of the \texttt{cforest} function.  We intend to do
so in the future by tackling some of the open conceptual issues described in
our previous replies.  But, the current \texttt{partykit::cforest} function
clearly shows that also implementations of random forests will benefit from
the unified tree infrastructure established in the \textbf{partykit} package.
